Inference for multivariate peaks over threshold models

### 2022-01-05 results.tex
asd

\begin{figure}[tb]
\begin{center}
    \centering
  \caption{Posterior predictive loss (Left) and energy score (right) for various models on simulated data.  Gen indicates baseline.\label{fig:simpples}}
  \begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[height=2in, width=\textwidth]{./images/simulation_ppl}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[height=2in, width=\textwidth]{./images/simulation_es}
  \end{subfigure}
\end{center}
\end{figure}

>>>>

% \begin{figure}[tb]
% \begin{center}
%     \centering
%   \caption{Posterior predictive loss (Left) and energy score (right) for various models on simulated data.  Gen indicates baseline.\label{fig:simpples}}
%   \begin{subfigure}[b]{0.48\textwidth}
%     \centering
%     \includegraphics[height=2in, width=\textwidth]{./images/simulation_ppl}
%   \end{subfigure}
%   %
%   \begin{subfigure}[b]{0.48\textwidth}
%     \centering
%     \includegraphics[height=2in, width=\textwidth]{./images/simulation_es}
%   \end{subfigure}
% \end{center}
% \end{figure}
\begin{figure}[tb]
    \centering
    \caption{Energy score (top) and Posterior Predictive Loss (bottom) for various models on simulated data with ascending count of mixture components (indicated by plot heading).  Gen indicates baseline.\label{fig:simpples}}
    \includegraphics[height=3in, width = \textwidth]{./images/simulation_score}
\end{figure}
